---
title: "Analysis"
format: 
    gfm:
        toc: true
        echo: true
        message: false
        warning: false
editor: visual

---

How have board games been rated by the BoardGameGeek (BGG) community over time? This analysis looks at historical games and their ratings on BGG.

```{r}
#| include: false
#| warning: false
#| message: false
#| label: setup
#| echo: true

# packages
library(tidyverse)
library(bggUtils)

# data
games = read_csv('data/processed/games_historical.csv')

# set custom ggplot theme
theme_set(
    bggUtils::theme_bgg()
)

```

# Data

The data comes from BoardGameGeek.com and contains `r nrow(games)` games.

```{r}

games |>
    sample_n(5)

```

```{r}
#| label: plot-games-by-year
#| warning: false
#| message: false

games |>
    filter(yearpublished > 1900) |>
    group_by(yearpublished) |>
    count() |>
    ggplot(aes(x=yearpublished, y=n))+
    geom_col()

```

The dataset contains games earlier than the 1900s, but the majority of games in the dataset were published in the last 30 years.

BoardGameGeek aggregates ratings by thousands of users.

- **average**: average rating on a 0-10 scale by all users that have rated the game

- **usersrated**: the number of users that have rated the game

- **averageweight**: complexity of a game on a 1-5 scale, with 1 being simple and 5 being complex

- **bayesaverage**: also known as the Geek rating, a Bayesian average of the community's average rating

# Questions

### What is the oldest game?

Find the oldest game in this dataset. Display its game_id, name, yearpublished.

```{r}
```

What is this game? Display its description.

```{r}

```

### What are the highest and lowest rated games?

Find the top 5 highest/lowest rated games based on *bayesaverage*. Display their game_id, name, yearpublished, bayesaverage, and averageweight.

```{r}

```


### What is the relationship between **average** and **averageweight**?

Find the correlation between the BGG average rating (*average*) and **averageweight**.

```{r}

```

Display this relationship visually by making a scatter plot with *averageweight* on the x axis and and average on the y axis. (It might help to jitter the x axis slightly for visibility).

```{r}

```

